\poem{Legacy}{Legacy = \frac{I \cdot A \cdot T^2}{F + M}}{\item $I$: \index{Impact}\textit{Impact}. The depth and breadth of positive change created in others' lives, communities, or society, representing the transformative power of one's choices and actions over time.
\item $A$: \index{Authenticity}\textit{Authenticity}. The degree to which one lives true to their values and principles, creating genuine connections and meaningful contributions that resonate beyond superficial achievements.
\item $T$: \index{Time}\textit{Time}. The duration and consistency of one's efforts and presence, squared to show how sustained commitment exponentially amplifies the lasting value of one's contributions.
\item $F$: \index{Fear}\textit{Fear}. The hesitation and self-doubt that prevents bold action and authentic expression, acting as a barrier that diminishes the courage needed to create meaningful change.
\item $M$: \index{Materialism}\textit{Materialism}. The excessive focus on wealth, status symbols, and temporary possessions that can distract from building relationships and contributions that truly endure beyond death.}{This equation reveals legacy as the beautiful multiplication of authentic impact sustained over time, divided by the forces that diminish our courage to act meaningfully. Impact and authenticity work together, amplified by time squared, showing how consistent, genuine effort compounds exponentially. Fear and materialism in the denominator represent the barriers that keep us from living boldly and focusing on what truly matters for eternity.}