\poem{Trust}{Trust = \frac{R \cdot C \cdot I^2}{B + F}}{\item $R$: \index{Reliability}\textit{Reliability}. The consistent demonstration of dependability through actions matching words, creating predictable patterns that form the foundation of trustworthy relationships.
\item $C$: \index{Consistency}\textit{Consistency}. The unwavering alignment between values, words, and actions over time, showing that someone's character remains stable across different situations and circumstances.
\item $I$: \index{Intimacy}\textit{Intimacy}. The depth of emotional connection and mutual understanding that allows for vulnerability, squared because deeper intimacy exponentially strengthens trust bonds.
\item $B$: \index{Betrayal}\textit{Betrayal}. Past experiences of broken promises or violated confidence that create protective barriers, making it harder to extend trust even when circumstances might warrant it.
\item $F$: \index{Fear}\textit{Fear}. The anxiety and apprehension about potential hurt or disappointment that naturally inhibits our willingness to open ourselves to others and extend vulnerability.}{This equation reveals trust as the delicate alchemy of human connection. Reliability and consistency multiply with the squared power of intimacy, showing how deeper bonds exponentially amplify trust. Yet this positive force must overcome the denominators of past betrayals and present fears - the protective walls we build around our hearts. Like a mathematical dance between hope and caution, trust emerges when our positive experiences with others outweigh our defensive instincts.}