\poem{Discovery}{Discovery = \frac{C \cdot I^{\alpha} \cdot
\ln(T+1)}{R + e^{-P}}}{\item $C$: \index{Curiosity}\textit{Curiosity}.
The burning flame of wonder that drives us to question, explore, and
seek answers beyond the comfortable boundaries of what we already know
and understand.
\item $I$: \index{Investigation}\textit{Investigation}. The systematic
pursuit of knowledge through careful observation, experimentation, and
analysis that transforms raw curiosity into meaningful insights.
\item $T$: \index{Time}\textit{Time}. The patient accumulation of
moments spent in contemplation and exploration, where persistence
allows understanding to slowly crystallize from confusion.
\item $R$: \index{Resistance}\textit{Resistance}. The stubborn
barriers of conventional thinking, fear of change, and comfort with
ignorance that stand guard against new revelations and understanding.
\item $P$: \index{Preparation}\textit{Preparation}. The foundation of
knowledge, skills, and mental readiness that enables the mind to
recognize and grasp profound truths when they finally reveal
themselves.}{This equation reveals discovery as the beautiful
convergence of human drive and temporal patience, divided by the
forces that oppose revelation. Curiosity multiplies with investigation
raised to the power of insight, while time's logarithmic nature shows
that each moment of exploration yields diminishing but essential
returns. Resistance anchors the denominator, yet preparation's
exponential decay demonstrates how readiness dissolves barriers,
allowing breakthrough moments to emerge from dedicated pursuit.}