\poem{Purpose}{Purpose = \frac{V \cdot A \cdot T^2}{R + S}}{\item $V$: \index{Values}\textit{Values}. Core beliefs and principles that define what matters most to an individual, serving as the fundamental compass that shapes decisions and actions throughout life.
\item $A$: \index{Action}\textit{Action}. The deliberate steps and behaviors taken to manifest one's intentions in the world, transforming abstract ideals into tangible reality through consistent effort and commitment.
\item $T$: \index{Time}\textit{Time}. The duration and investment of moments dedicated to meaningful pursuits, where sustained engagement amplifies purpose exponentially as shown by the squared relationship.
\item $R$: \index{Resistance}\textit{Resistance}. External obstacles and internal doubts that create friction against purposeful living, including societal expectations, fear of failure, and competing priorities that dilute focus.
\item $S$: \index{Stagnation}\textit{Stagnation}. The tendency toward inertia and comfort zones that prevents growth and meaningful engagement, representing the gravitational pull of routine that opposes purposeful transformation.}{This equation reveals purpose as the sacred intersection of values and action, amplified by time's compound power, yet tempered by life's inevitable resistances. When our deepest values align with consistent action over sustained periods, purpose emerges with exponential force. However, external resistance and internal stagnation act as denominators, reminding us that clarity of purpose requires overcoming both the world's obstacles and our own inertia to achieve meaningful existence.}