\poem{Strength}{Strength = \frac{R \cdot W^2 \cdot P}{A + F}}{\item $R$: \index{Resolve}\textit{Resolve}. The unwavering determination and commitment to one's values and goals, serving as the foundational force that drives us forward through challenges and setbacks.
\item $W$: \index{Wisdom}\textit{Wisdom}. The profound understanding gained through experience and reflection, squared to show its exponential impact on our ability to navigate complexity with grace and insight.
\item $P$: \index{Purpose}\textit{Purpose}. The deep sense of meaning and direction that gives weight to our actions, transforming ordinary efforts into extraordinary achievements through aligned intention.
\item $A$: \index{Adversity}\textit{Adversity}. The sum of external challenges, obstacles, and hardships that test our limits, serving as resistance that either weakens us or, when overcome, makes us stronger.
\item $F$: \index{Fear}\textit{Fear}. The internal doubts, anxieties, and hesitations that can paralyze progress, acting as a denominator that diminishes strength when allowed to dominate our thoughts.}{This equation reveals strength as the harmonious interplay of inner resources overcoming life's resistances. Resolve provides the foundation, while wisdom's squared influence shows how understanding compounds exponentially. Purpose amplifies every effort with meaning. Together, these forces triumph over adversity and fear, demonstrating that true strength emerges not from avoiding challenges, but from transforming them into catalysts for growth and character.}