\poem{Grief}{Grief = \frac{L \cdot M \cdot e^{-\alpha t}}{A + R}}{\item $L$: \index{Love}\textit{Love}. The depth of emotional connection and attachment to what was lost, serving as the foundation from which grief springs and determining its initial intensity.
\item $M$: \index{Memories}\textit{Memories}. The collection of shared experiences, moments, and emotional imprints that keep the lost connection alive in our hearts and minds, amplifying the sense of absence.
\item $t$: \index{Time}\textit{Time}. The natural healer that gradually softens grief's sharp edges through the exponential decay function, though never fully erasing the love that created it.
\item $A$: \index{Acceptance}\textit{Acceptance}. The gradual acknowledgment and integration of loss into one's life narrative, which serves as a denominator that reduces grief's overwhelming intensity over time.
\item $R$: \index{Resilience}\textit{Resilience}. The inner strength and adaptive capacity to navigate through sorrow, representing our ability to find meaning and continue living despite profound loss.}{This equation reveals grief as love's echo through time's corridor. The intensity of our sorrow mirrors the depth of our connection - greater love yields deeper grief. Memories amplify this ache, keeping loss vivid in our hearts. Yet time's exponential decay gently softens grief's sharp edges, while acceptance and resilience in the denominator gradually transform overwhelming sorrow into tender remembrance, proving that grief is simply love with nowhere to go.}