\poem{Heartbreak}{Heartbreak = \frac{A \cdot T^2 \cdot e^{-R \cdot t}}{M}}{\item $A$: \index{Attachment}\textit{Attachment}. The depth of emotional bond and connection formed with another person, measuring how intertwined two lives became through shared experiences and intimate moments.
\item $T$: \index{Time}\textit{Time}. The duration of the relationship, squared to show how deeper connections exponentially amplify the pain when severed, as memories accumulate like compound interest.
\item $R$: \index{Resilience}\textit{Resilience}. One's capacity for emotional recovery and adaptation, acting as a healing coefficient that gradually diminishes heartbreak's intensity through self-compassion and growth.
\item $t$: \index{Recovery}\textit{Recovery}. The time elapsed since the loss occurred, representing the natural healing process where each passing moment slowly transforms raw pain into wisdom and acceptance.
\item $M$: \index{Meaning}\textit{Meaning}. The sense of purpose and understanding one finds in the experience, serving as a protective denominator that transforms suffering into profound life lessons and growth.}{This equation reveals heartbreak as a complex interplay of love's remnants and healing forces. Attachment and time create the initial devastating impact, amplified exponentially by the depth of connection. Yet resilience acts as nature's gentle decay function, gradually softening the blow as recovery time passes. Meaning serves as the transformative denominator, showing how finding purpose in pain ultimately diminishes its power over us.}