\poem{Regret}{Regret = \frac{I \cdot T^2 \cdot \ln(C + 1)}{A \cdot e^{-W}}}{\item $I$: \index{Impact}\textit{Impact}. The magnitude of consequences from our choices, representing how significantly a decision altered the trajectory of our lives or affected others around us.
\item $T$: \index{Time}\textit{Time}. The duration since the regretful decision was made, appearing squared to show how regret compounds exponentially as years pass and opportunities fade.
\item $C$: \index{Counterfactuals}\textit{Counterfactuals}. The number of alternative scenarios we imagine could have unfolded, with logarithmic growth showing how even small increases in imagined possibilities amplify regret.
\item $A$: \index{Acceptance}\textit{Acceptance}. Our capacity to make peace with past decisions and their outcomes, serving as a denominator that reduces regret through emotional maturity and self-forgiveness.
\item $W$: \index{Wisdom}\textit{Wisdom}. The understanding gained from life experience that helps contextualize past decisions, appearing in an exponential decay function that powerfully diminishes regret's hold.}{This equation reveals regret as a complex interplay of temporal and emotional forces. Impact and time multiply to create the foundation of remorse, while counterfactual thinking adds logarithmic complexity to our suffering. Yet wisdom acts as an exponential healer, and acceptance serves as our shield. The mathematics shows that while regret may grow with time's square, wisdom's exponential power ultimately offers redemption, teaching us that understanding transforms pain into profound human growth.}