\poem{War}{War = \frac{P^2 \cdot R \cdot e^{I}}{T + H}}{\item $P$: \index{Power}\textit{Power}. The desire for dominance and control over resources, territory, or ideology, squared to show how power-seeking amplifies exponentially in competitive situations.
\item $R$: \index{Resources}\textit{Resources}. Scarcity of essential materials, land, or wealth that drives competition between groups, acting as a multiplier that intensifies conflicts over survival and prosperity.
\item $I$: \index{Ideology}\textit{Ideology}. Fundamental beliefs and worldviews that create irreconcilable differences, exponentially escalating conflicts when groups view their values as absolute and non-negotiable.
\item $T$: \index{Trust}\textit{Trust}. The foundation of diplomatic relations and peaceful coexistence, serving as a denominator that reduces conflict potential when present between opposing parties.
\item $H$: \index{Humanity}\textit{Humanity}. Compassion, empathy, and recognition of shared human dignity that acts as a restraining force against violence, diminishing war's likelihood through moral consideration.}{This equation reveals war as the tragic result when human ambitions collide with scarcity while moral restraints weaken. Power-seeking squared with resource competition, amplified exponentially by ideological fervor, creates devastating conflict. Yet trust and humanity serve as denominators—the greater our capacity for empathy and diplomatic faith, the more we can contain war's destructive potential and choose peace over violence.}