\poem{Madness}{Madness = \frac{S^2 \cdot e^{-R/T}}{P \cdot \log(C + 1)}}{\item $S$: \index{Stress}\textit{Stress}. Accumulated psychological pressure from life's demands, trauma, and overwhelming circumstances that compound exponentially to fracture mental stability.
\item $R$: \index{Resilience}\textit{Resilience}. The mind's capacity to withstand psychological pressure and recover from adversity, acting as a protective force against mental breakdown and chaos.
\item $T$: \index{Time}\textit{Time}. The duration over which psychological forces act, where prolonged exposure to stress without relief accelerates the descent into madness and mental fragmentation.
\item $P$: \index{Purpose}\textit{Purpose}. One's sense of meaning and direction in life, serving as an anchor to reality that helps maintain psychological coherence and prevents complete mental dissolution.
\item $C$: \index{Connection}\textit{Connection}. The strength of social bonds and relationships that tether the mind to shared reality, providing external validation and support against isolation and delusion.}{This equation reveals madness as stress squared multiplied by an exponential decay of resilience over time, all divided by the stabilizing forces of purpose and logarithmic connection. As stress compounds and resilience weakens with prolonged exposure, madness intensifies exponentially. Yet purpose and human connection act as denominators, their presence reducing madness's grip on the psyche through meaning and shared reality.}