\poem{Obsession}{Obsession = \frac{I^2 \cdot T \cdot \ln(D+1)}{R \cdot e^{-S}}}{\item $I$: \index{Interest}\textit{Interest}. The initial spark of fascination or attraction that captures attention, squared to show how even small interests can exponentially amplify into consuming focus.
\item $T$: \index{Time}\textit{Time}. The duration of sustained attention and mental energy invested in the object of fixation, acting as a multiplier that intensifies obsessive patterns over extended periods.
\item $D$: \index{Desire}\textit{Desire}. The underlying longing or craving that fuels persistent thoughts, with logarithmic growth representing how desire builds gradually but can reach overwhelming levels.
\item $R$: \index{Rationality}\textit{Rationality}. The logical thinking and balanced perspective that serves as a moderating force, helping to maintain healthy boundaries and realistic expectations in the denominator.
\item $S$: \index{Satisfaction}\textit{Satisfaction}. The level of fulfillment and contentment already achieved, where higher satisfaction exponentially reduces obsessive tendencies through the negative exponential function.}{This equation reveals obsession as the mathematical dance between desire and restraint. Interest squares itself, creating exponential amplification, while time stretches the fixation across moments. Desire grows logarithmically, building slowly then surging powerfully. Yet rationality stands guard in the denominator, offering balance, while satisfaction's exponential decay shows how fulfillment can dissolve even the most consuming obsessions into peaceful acceptance.}