\poem{Love}{Love = \frac{A \cdot E \cdot T^2}{V + F}}{\item $A$: \index{Affection}\textit{Affection}. The tender feelings of fondness and warmth expressed through words, actions, and presence, serving as the foundational building blocks of emotional intimacy.
\item $E$: \index{Empathy}\textit{Empathy}. The ability to understand and share another's feelings, creating bridges of understanding that multiply the connection between hearts and minds.
\item $T$: \index{Time}\textit{Time}. The precious moments invested together, squared to show how shared experiences compound exponentially, deepening bonds through accumulated memories and growth.
\item $V$: \index{Vulnerability}\textit{Vulnerability}. The courage required to open one's heart completely, which paradoxically can both strengthen love through authenticity and create barriers through fear of hurt.
\item $F$: \index{Fear}\textit{Fear}. The protective instinct that guards against emotional pain, often creating resistance to love's full expression while serving as a necessary caution in relationships.}{This equation captures love as the product of positive emotional forces divided by protective barriers. Affection, empathy, and time investment multiply to create strong bonds, while vulnerability and fear act as denominators that can limit love's full expression. The mathematical relationship shows that as we overcome our fears and allow ourselves to be vulnerable, love grows exponentially through genuine care and shared time.}