\poem{Freedom}{Freedom = \frac{A \cdot W^2}{R + C \cdot e^{-T}}}{\item $A$: \index{Autonomy}\textit{Autonomy}. The fundamental ability to govern oneself and make independent decisions, serving as the foundational force that drives all expressions of personal liberty.
\item $W$: \index{Will}\textit{Will}. The inner strength and determination to pursue one's chosen path, squared to emphasize how willpower compounds exponentially when channeled with purpose.
\item $R$: \index{Resistance}\textit{Resistance}. External societal, political, or cultural forces that oppose individual liberty, creating barriers that must be overcome to achieve true freedom.
\item $C$: \index{Conditioning}\textit{Conditioning}. Internal psychological limitations from past experiences, beliefs, and learned behaviors that constrain our perception of what choices are possible.
\item $T$: \index{Time}\textit{Time}. The duration of conscious effort toward liberation, where sustained practice gradually weakens the grip of conditioning through exponential decay.}{This equation reveals freedom as the delicate interplay between inner strength and external constraints. Autonomy and willpower multiply in the numerator, showing how personal agency grows exponentially with determination. Below, resistance represents societal barriers, while conditioning decays over time through conscious effort. As we persist in our journey toward liberation, the exponential term diminishes, allowing our authentic will to flourish against diminishing internal limitations.}