\poem{Peace}{Peace = \frac{H \cdot M^2 \cdot e^{-T}}{C + F}}{\item $H$: \index{Harmony}\textit{Harmony}. The degree of alignment between one's values, actions, and environment, creating a foundation of consistency that amplifies the potential for peaceful existence through coherent living.
\item $M$: \index{Mindfulness}\textit{Mindfulness}. The practice of present-moment awareness and conscious attention, squared to emphasize its compounding effect on peace as deeper awareness creates exponentially greater serenity.
\item $T$: \index{Time}\textit{Time}. The passage of temporal existence that, when released through acceptance, allows peace to flourish as we stop clinging to past regrets and future anxieties through exponential decay.
\item $C$: \index{Conflict}\textit{Conflict}. Internal and external discord that creates resistance to peaceful states, acting as a denominator that diminishes peace by fragmenting attention and creating emotional turbulence.
\item $F$: \index{Fear}\textit{Fear}. Anticipatory anxiety about potential threats or losses that blocks peaceful acceptance, serving as a barrier in the denominator that prevents the full flowering of tranquil consciousness.}{This equation reveals peace as an emergent property of harmonious living amplified by mindful awareness. As harmony aligns our being and mindfulness deepens exponentially, peace grows. The exponential decay of time's grip shows how releasing temporal attachments liberates us. Yet conflict and fear in the denominator remind us that peace diminishes when we're caught in discord or anxiety, making this a delicate dance of consciousness.}