\poem{Love}{Love = \frac{A \cdot E \cdot T^2}{V + F}}{\item $A$: \index{Affection}\textit{Affection}. The tender feelings of fondness and warmth expressed through gestures, words, and presence that form the foundation of emotional intimacy between people.
\item $E$: \index{Empathy}\textit{Empathy}. The ability to understand and share another's feelings, creating emotional resonance that deepens connection and fosters mutual understanding in relationships.
\item $T$: \index{Time}\textit{Time}. The investment of moments shared together, squared to represent how quality time compounds exponentially, building memories and strengthening emotional bonds over duration.
\item $V$: \index{Vulnerability}\textit{Vulnerability}. The emotional exposure and risk of being hurt that acts as a protective barrier, potentially limiting the full expression of love when fear overshadows openness.
\item $F$: \index{Fear}\textit{Fear}. The anxiety and apprehension about emotional pain or rejection that creates resistance to love, serving as a denominator that can diminish love's intensity and growth.}{This equation captures love as the product of positive emotional forces divided by protective barriers. Affection, empathy, and time investment multiply to create strong bonds, while vulnerability and fear act as denominators that can limit love's full expression. The mathematical relationship shows that as we overcome our fears and allow ourselves to be vulnerable, love grows exponentially through genuine care and shared time.}