\poem{Romance}{Romance = \frac{A \cdot E \cdot T^2}{V + F}}{\item $A$: \index{Affection}\textit{Affection}. The tender care and warmth expressed through gestures, words, and presence, forming the foundation of emotional intimacy that nurtures romantic connection.
\item $E$: \index{Empathy}\textit{Empathy}. The ability to understand and share your partner's feelings, creating emotional resonance that deepens connection and builds trust in romantic relationships.
\item $T$: \index{Time}\textit{Time}. The precious moments shared together, squared to represent how quality time compounds exponentially, creating memories and strengthening romantic bonds through shared experiences.
\item $V$: \index{Vulnerability}\textit{Vulnerability}. The emotional risk and openness required in love, which paradoxically both threatens and enables deep connection, acting as a barrier that must be overcome for true intimacy.
\item $F$: \index{Fear}\textit{Fear}. The apprehension of rejection, heartbreak, or loss that creates emotional walls, diminishing love's potential by preventing full emotional investment and authentic connection.}{This equation captures love as the product of positive emotional forces divided by protective barriers. Affection, empathy, and time investment multiply to create strong bonds, while vulnerability and fear act as denominators that can limit love's full expression. The mathematical relationship shows that as we overcome our fears and allow ourselves to be vulnerable, love grows exponentially through genuine care and shared time.}