\poem{Time}{Time = \frac{M \cdot e^{P \cdot \ln(A)}}{R + S}}{\item $M$: \index{Mindfulness}\textit{Mindfulness}. The degree of present-moment awareness and conscious attention we bring to our experiences, amplifying our perception of time's richness and depth.
\item $P$: \index{Purpose}\textit{Purpose}. The sense of meaning and direction in our activities, acting as an exponential multiplier that transforms how we experience the passage of moments.
\item $A$: \index{Attention}\textit{Attention}. The focused cognitive resource we allocate to experiences, determining the quality and intensity of our temporal perception through logarithmic scaling.
\item $R$: \index{Routine}\textit{Routine}. The habitual patterns and repetitive behaviors that compress our sense of time, making days blur together in an undifferentiated stream of familiarity.
\item $S$: \index{Stress}\textit{Stress}. The psychological pressure and anxiety that distorts temporal perception, either accelerating time through overwhelm or freezing it in moments of crisis.}{This equation reveals time as a dance between consciousness and circumstance. Mindfulness multiplies with purpose raised to the power of attention, creating exponential richness in our temporal experience. Yet routine and stress conspire as denominators, compressing our perception into mechanical repetition. When we cultivate deep presence and clear purpose while minimizing life's numbing patterns, time transforms from a scarce resource into an abundant canvas for meaningful existence.}