\poem{Revenge}{Revenge = \frac{P \cdot I^2 \cdot e^{-T/\tau}}{J + M}}{\item $P$: \index{Pain}\textit{Pain}. The depth of emotional or physical suffering inflicted by the original transgression, serving as the primary catalyst that ignites the vengeful impulse within the human heart.
\item $I$: \index{Injustice}\textit{Injustice}. The perceived magnitude of unfairness or moral violation experienced, which amplifies revenge through its squared relationship, making small injustices feel exponentially larger.
\item $T$: \index{Time}\textit{Time}. The duration elapsed since the original wound was inflicted, representing how temporal distance naturally diminishes the burning desire for retribution through healing.
\item $J$: \index{Justice}\textit{Justice}. The degree to which proper legal or moral resolution has been achieved through legitimate channels, serving as a counterbalance that reduces the need for personal vengeance.
\item $M$: \index{Maturity}\textit{Maturity}. The level of emotional wisdom and perspective that comes with personal growth, enabling one to transcend base impulses and choose forgiveness over retaliation.}{This equation reveals revenge as an exponential decay of pain and injustice over time, tempered by wisdom and justice. The squared injustice term shows how perceived wrongs magnify disproportionately, while the exponential time decay reflects healing's natural progression. As justice is served and maturity grows, revenge diminishes—teaching us that time, wisdom, and proper resolution are the antidotes to vengeance's destructive fire.}