\poem{Serenity}{Serenity = \frac{A \cdot M^2}{T + R \cdot e^{C}}}{\item $A$: \index{Acceptance}\textit{Acceptance}. The practice of embracing reality as it is without resistance, allowing circumstances to flow naturally while releasing the need to control outcomes.
\item $M$: \index{Mindfulness}\textit{Mindfulness}. Present-moment awareness that anchors consciousness in the here and now, multiplied by itself to show its compounding effect on inner peace and clarity.
\item $T$: \index{Turmoil}\textit{Turmoil}. External chaos and internal emotional disturbance that disrupts peace, representing the storms of life that challenge our equanimity and test our resilience.
\item $R$: \index{Resistance}\textit{Resistance}. The tendency to fight against what is, creating internal friction that exponentially amplifies suffering when combined with attachment to specific outcomes.
\item $C$: \index{Craving}\textit{Craving}. Intense desires and attachments that fuel resistance, appearing as an exponent to show how wanting things to be different exponentially increases our inner conflict.}{This equation reveals serenity as the graceful dance between acceptance and awareness, divided by the forces that disturb our peace. Acceptance and mindfulness squared work together in the numerator, showing how present-moment awareness compounds its own power. Below, turmoil represents life's inevitable challenges, while resistance multiplied by exponential craving shows how our internal reactions amplify suffering far beyond external circumstances.}