\poem{Happiness}{Happiness = \frac{G \cdot P^2 \cdot e^{-A}}{S + 1}}{\item $G$: \index{Gratitude}\textit{Gratitude}. The practice of recognizing and appreciating positive aspects of life, acting as a fundamental multiplier that amplifies joy and transforms ordinary moments into sources of fulfillment.
\item $P$: \index{Purpose}\textit{Purpose}. The sense of meaning and direction in life, squared to reflect its exponential impact on happiness when one aligns actions with deeply held values and meaningful goals.
\item $A$: \index{Attachment}\textit{Attachment}. The degree of clinging to outcomes and expectations, where excessive attachment creates suffering through the exponential decay function, diminishing happiness as we resist life's flow.
\item $S$: \index{Suffering}\textit{Suffering}. The accumulated pain, loss, and hardship experienced in life, positioned in the denominator where it can diminish happiness but never completely eliminate it due to the constant.}{This equation reveals happiness as an emergent property of conscious living. Gratitude multiplies with purpose squared, showing how meaning exponentially amplifies joy. The exponential decay of attachment teaches us that letting go creates space for contentment to flourish. Suffering, while present in the denominator, cannot reduce happiness to zero—the constant ensures resilience remains. This mathematical poetry demonstrates that happiness isn't the absence of pain, but the cultivation of appreciation, purpose, and acceptance that transcends our inevitable struggles.}